### 2014-11-05 SP_simul.Rmd
Update abstract manuscript up to results and figure 1-2

## Plots for publication uniform SAD

@@

# Plot of the uniform and randomized spatial pattern for a uniform SAD with 64 species and side=256
#

g <- plotSAD_SpatPat(64,256,"U")
g 
setwd("..")
ggsave("spat_Unif64_256.png", width=8,height=6,units="in",dpi=600)
setwd("Simul")

#
# Plots of Dq with uniform SAD and 20 repetitions!
#
unique(DqT$SAD)
#DqT$Type[DqT$Type=="SRS"] <- "DqSRS"
#DqT$Type[DqT$Type=="rnzSRS"] <- "rnzDqSRS"

rm(Dq1,Dq2,fname,fname1)

g <- plotDq_Side_Sp(DqT,256,64,"Uniform")
g
setwd("..")
ggsave("Dq_Unif64_256.png", width=8,height=4,units="in",dpi=600)

@@

#
# Plot R2 for dqSAD dqSRS
#
g <- plotR2Dq_Side_Sp(DqT,256,64,"Uniform")
g
ggsave("R2Dq_Unif_64_256.png", width=8,height=6,units="in",dpi=600)

@@

#!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!! GENERA MAL 
# save_matrix_as_sed
# 
# Le falta un \n

g <- plotSAD_SpatPat(64,256,"L")
g 
setwd("..")
ggsave("spat_Logser64_256.png", width=8,height=6,units="in",dpi=600)

unique(DqT$SAD)

g <- plotDq_Side_Sp(DqT,256,64,"Logseries")
g
ggsave("Dq_Logser64_256.png", width=8,height=4,units="in",dpi=600)

@@

#
# Plot R2 for dqSAD dqSRS
#
g <- plotR2Dq_Side_Sp(DqT,256,64,"Logseries")
g
ggsave("R2Dq_Logser_64_256.png", width=8,height=6,units="in",dpi=600)

@@

>>>>

## Plots for publication uniform/Logseries SAD

@@

# Plot of the Regular and Randomized spatial pattern for a uniform & Logseries SAD with 64 species and side=256
#
g <- plotSAD_SpatPat(64,256,"B")
g

#g <- plotSAD_SpatPat(64,256,"U")
#g 
setwd("..")
ggsave("spat_UniLog64_256.png", width=8,height=6,units="in",dpi=600)
setwd("Simul")

#
# Plots of Dq with uniform/Logseries SAD and 10 repetitions!
#
unique(DqT$SAD)

g <- plotDq_Side_Sp(DqT,256,64,"B")
g
setwd("..")
ggsave("Dq_UniLog64_256.png", width=8,height=6,units="in",dpi=600)

g <- plotDq_Side_Sp(DqT,256,0,"B")
g
ggsave("Dq_UniLog_NumSp_256.png", width=8,height=6,units="in",dpi=600)

#g <- plotDq_Side_Sp(DqT,256,64,"Uniform")
#g

@@

#
# Plot R2 for dqSAD dqSRS for uniform & Logseries
#
g <- plotR2Dq_Side_Sp(DqT,256,64,"B") 
g
ggsave("R2Dq_UniLog_64_256.png", width=8,height=6,units="in",dpi=600)

g <- plotR2Dq_Side_Sp(DqT,256,64,"Uniform")
g

@@

#g <- plotSAD_SpatPat(64,256,"L")
#g 
#setwd("..")
#ggsave("spat_Logser64_256.png", width=8,height=6,units="in",dpi=600)

#unique(DqT$SAD)

#g <- plotDq_Side_Sp(DqT,256,64,"Logseries")
#g
#ggsave("Dq_Logser64_256.png", width=8,height=4,units="in",dpi=600)

@@

#
# Plot R2 for dqSAD dqSRS
#
#g <- plotR2Dq_Side_Sp(DqT,256,64,"Logseries")
#g
#ggsave("R2Dq_Logser_64_256.png", width=8,height=6,units="in",dpi=600)

@@

g <- plotR2Dq_Side_Sp(DqT,0,0,"Neutral")
g
